---
title: "Homework 6"
author: "Wenxin Tian"
date: "`r Sys.Date()`"
output: github_document
---

```{r}
library(tidyverse)
library(modelr)
```

## Problem 1:

__Data Import:__

```{r}
homicide =
  read_csv("./data/homicide-data.csv") |>
  mutate(
    city_state = paste(city, state, sep = ", "),
    resolved = as.numeric(disposition == "Closed by arrest")
  ) |>
  filter(
    !city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL"),
    victim_race %in% c("White", "Black")
  ) |>
  mutate(victim_age = as.numeric(victim_age)) |>
  drop_na(victim_age) |>
  select(resolved, victim_age, victim_race, victim_sex, city_state)
  
```

__GLM:__

```{r}
baltimore = homicide |>
  filter(city_state == "Baltimore, MD")

baltimore_glm = 
  baltimore |>
  glm(resolved ~ victim_age + victim_race + victim_sex, data = _, family = binomial())


# Confidence interval??

baltimore_glm |>
  broom::tidy() |> 
  mutate(OR = exp(estimate)) |>
  select(term, log_OR = estimate, OR, p.value) |> 
  knitr::kable(digits = 3)

baltimore |>
  add_predictions(baltimore_glm) |>
  mutate(prob = boot::inv.logit(pred))
```

## Problem 2:

__Data Import:__

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

__Bootstrapping:__

```{r}
bootstraps =
  weather_df |>
  bootstrap(5000) 

# r2:
r2 =
  bootstraps |>
  mutate(
    models = map(strap, \(df) lm(tmax ~ tmin + prcp, data = df) ),
    results = map(models, broom::glance)) |> 
  select(-strap, -models) |> 
  unnest(results)

# log beta:

log_beta =
  bootstraps |>
  mutate(
    models = map(strap, \(df) lm(tmax ~ tmin + prcp, data = df) ),
    results = map(models, broom::tidy)) |> 
  select(-strap, -models) |> 
  unnest(results)
```

__Plot:__

```{r}
# Note: negative log transformation?

# intercept: beta0, tmin: beta1, prcp: beta3
log_beta |>
  pivot_wider(names_from = term, values_from = estimate) |>
  group_by(.id) |>
  mutate(intercept = `(Intercept)`) |>
  fill(intercept, tmin, prcp, .direction = 'up') |>
  fill(intercept, tmin, .direction = 'down') |>
  summarize(log_beta = log(intercept * tmin)) |>
  distinct() |>
  ggplot(aes(x = log_beta)) +
  geom_density() +
  labs(title = "Log Beta")

r2 |>
  ggplot(aes(x = r.squared)) +
  geom_density() +
  labs(title = "r squared")
```

For both the r squared and log(beta0 * beta1) estimates, a normal distribution was seen. The log beta distribution is centered around 2.10, whereas the r2 distribution is centered around 0.91, which indicates a strong correlation between predictor and outcome. One thing to note is that the product of beta 1 and beta 2 are often negative and cannot be log transformed, so I guess the question meant to ask log(beta0 * beta1), which is positive. 

__Quantile:__

```{r}
# Quantile for r2:
quantile(r2$r.squared, probs = c(0.025, 0.975))

# Quantile for log beta:
logbeta_clean = 
  log_beta |>
  pivot_wider(names_from = term, values_from = estimate) |>
  group_by(.id) |>
  mutate(intercept = `(Intercept)`) |>
  fill(intercept, tmin, prcp, .direction = 'up') |>
  fill(intercept, tmin, .direction = 'down') |>
  summarize(log_beta = log(intercept * tmin)) |>
  distinct()

quantile(logbeta_clean$log_beta, probs = c(0.025, 0.975))
```

